---
title: "multipage pdf with Geosyntec format"
output: html_document
date: "2022-09-14"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(dpi=300)

```

## Multipage TSP plots generated on Geosyntec template

### Next steps
1) Make ggplot with dialed in formatting
  * Figure numbers
  * either lock size of plot area or put legend to the right
2) Pull table from queries with any filtering steps that are needed
3) Other stuff /ideas
  * prevent plot size from changing when legend size changes
  * Version that will facet with GW plots (maybe an ifelse to choose between GW and non-GW)
  * move variable assignment to top for ease of use/changing
  * add "in_filename" and "out_filename" as variables
 

```{r, include = FALSE}
#include = FALSE will hide everything in the code chunk, echo=FALSE will hide code but show plots, etc.
 
################################################
# Author: Summer Broeckx-Smith, Caroline Conrad, Michael Maniscalco
# Date Created: September 14, 2022
# Last modified: September 26, 2022
################################################
```


### Load libraries
* I think some of these packages aren't being used in this code anymore

```{r libraries, message=FALSE}
library(tidyverse)
library(magick)
library(janitor)
library(ggpubr)
library(cowplot)
library(gridExtra)
library(here)
library(grid)
library(readxl)
library(ggtext)
library(egg)
# library(Kendall)
library(kableExtra)
# library(tinytex)
library(ggh4x) #THIS PACKAGE IS AWESOME - ggplot2 hacks!
```


### Set Variables

```{r}
figure_office <- "Santa Barbara"
figure_date <- "December 2022"
figure_file_path <- "C:/Users/Michael.Maniscalco/OneDrive - Geosyntec/Documents"

```

### Load qryTSPPlotList 

```{r qry load}
connect_to_access_dbi <- function(db_file_path)  {
  require(DBI)
  # make sure that the file exists before attempting to connect
   if (!file.exists(db_file_path)) {
     stop("DB file does not exist at ", db_file_path)
   }
  # Assemble connection strings
  dbq_string <- paste0("DBQ=", db_file_path)
  driver_string <- "Driver={Microsoft Access Driver (*.mdb, *.accdb)};"
  db_connect_string <- paste0(driver_string, dbq_string)

  myconn <- dbConnect(odbc::odbc(),
                      .connection_string = db_connect_string)
  return(myconn)
}


con<- connect_to_access_dbi("P:/GIS/County of Santa Barbara RRWMD/Database/Plots/Graph_AllSites_County_of_SB.accdb")

qryTSP_list <- tbl(con, "qryTSPPlotList") %>%
  data.frame()
dbDisconnect(con)

rm(con, connect_to_access_dbi)
```

### Load data

```{r data}
df_no_dupes <- read_excel("P:/!Users_Public/Broeckx-Smith/Excel TSP Revamp/Dummy Input Data/qryHLE_Basic_Data_Query_No_Dups_06a_Final_with_Min_RL_NDs_CoSB_DummyInputs.xlsx") %>%
    mutate(`Date Sampled`=as.Date(`Date Sampled`),
           SigFigResult= as.numeric(gsub(",","",SigFigResult)),
           Detect=factor(Detect,
                         levels = c(0, 1),
                         labels = c("Non-detect", "Detect"),),
           Loc=str_replace(string=Loc, pattern= "FCCL-","")
           ) 

df_GWLs <- read_excel("P:/!Users_Public/Broeckx-Smith/Excel TSP Revamp/Dummy Input Data/tblJDW_Groundwater_GW_Levels_CoSB_DummyInputs.xlsx")
```

### Filter by qryTSP

```{r filter}
qryTSP_list_taj <- qryTSP_list %>%
  filter(Site =="Tajiguas Landfill")

df_no_dupes <- left_join(qryTSP_list_taj, df_no_dupes, by ="Analyte")  #Use qry parameter to filter data

missing_Area <- df_no_dupes %>%
  filter(is.na(Area))

df_no_dupes <- df_no_dupes %>%
  filter(!is.na(Area))
  
  
df_noDup_list <-df_no_dupes %>%
  split( df_no_dupes , f = df_no_dupes$Analyte) # split dataframe into list by analyte

```

### Create pallette

```{r pallette}
```

### Formatting functions for time series plot

```{r format}
# Maybe if we hack the y-axis text into being rotated it will deal with the width spacing inconsistencies introduced by the varied units
# Scientific notation could work too, but I have been told that is not ideal in for readers  note to MAM= check for solution in July work
# https://stackoverflow.com/questions/1330989/rotating-and-spacing-axis-labels-in-ggplot2
rotatedAxisElementText = function(angle,position='x'){
  angle     = angle[1]; 
  position  = position[1]
  positions = list(x=0,y=90,top=180,right=270)
  if(!position %in% names(positions))
    stop(sprintf("'position' must be one of [%s]",paste(names(positions),collapse=", ")),call.=FALSE)
  if(!is.numeric(angle))
    stop("'angle' must be numeric",call.=FALSE)
  rads  = (angle - positions[[ position ]])*pi/180
  hjust = 0.5*(1 - sin(rads))
  vjust = 0.5*(1 + cos(rads))
  element_text(angle=angle,vjust=vjust,hjust=hjust)
}


#Outsourced script to make axis auto-breaks for log scale
prettyLogs <- function(x){
                          pretty_range <- range(x[x > 0])
                          pretty_logs <- 10^(-10:10)
                          log_index <- which(pretty_logs < pretty_range[2] &
                                               pretty_logs > pretty_range[1])
                          log_index <- c(log_index[1]-1,log_index, log_index[length(log_index)]+1)
                          pretty_logs_new <-  pretty_logs[log_index]
                          return(pretty_logs_new)
                         }

#Outsourced script to format 10^x for log scale
fancyNumbers <- function(n){
                            nNoNA <- n[!is.na(n)]
                            x <-gsub(pattern = "1e",replacement = "10^",
                                     x = format(nNoNA, scientific = TRUE))
                            exponents <- as.numeric(sapply(strsplit(x, "\\^"), function(j) j[2]))
                            
                            base <- "10^"
                            exponents[base == "1" | base == "10"] <- ""
                            textNums <- rep(NA, length(n))
                            textNums[!is.na(n)] <- paste0(base,exponents)
                            
                            textReturn <- parse(text=textNums)
                            return(textReturn)
                          }
```

### Set custom theme

```{r theme}
#### set theme
  #   # text=element_text(family="Times"), 
  #       panel.background = element_rect(fill='transparent'), #transparent panel bg
  #       plot.background = element_rect(fill='transparent', color=NA), #transparent plot bg
  #       plot.margin=unit(c(0,0,0,0), 'inches'),
  #       panel.border = element_rect(colour = "black", fill=NA, size=1),
  #       panel.grid.major = element_line(linetype = "blank"), 
  #       panel.grid.minor = element_line(linetype = "blank"), 
  #       plot.title = element_text(size=12),
  #       axis.title = element_text(size = 12), 
  #       axis.text = element_text(size = 10, colour = "black"), 
  #       axis.line = element_line(colour = "black"), 
  #       axis.ticks = element_line(size = 1), 
  #       legend.title = element_blank(),
  #       legend.text = element_text(size = 8),
  #       legend.key = element_rect(fill = NA), 
  #       legend.background = element_blank(),
  #       legend.key.width =unit(0.15, units = "cm"),
  #       legend.key.height =unit(0.15, units = "cm"),
  #       axis.title.y = element_blank(),
  #       axis.text.x = element_text(angle = 45, vjust = 0.85, hjust = 0.95),
  #       legend.text.align= 0,
  #       legend.position = "bottom", 
  #       legend.justification = "left",
  #       legend.direction = "vertical",)
theme_set(
  theme(
    panel.background = element_rect(fill='transparent'), #transparent panel bg
    plot.background = element_rect(fill='transparent', color=NA), #transparent plot bg
    panel.border = element_rect(colour = "black", fill=NA, size=1),
    panel.grid.major = element_line(linetype = "blank"), 
    panel.grid.minor = element_line(linetype = "blank"), 
# panel.grid.major.y = element_line(color = "gray70"),
# panel.border = element_rect(color = "grey5", fill = NA),
    plot.margin = unit(c(0, 5.5, 0, 5.5), "pt"),
    axis.title.y = element_text(margin = margin(r=10), face = "bold", size = 12, angle = 90),
    axis.title.y.right = element_text(vjust=2),
    axis.text.y = element_text(face = "bold",  size = 9),
    axis.text.x = element_text(margin = margin(t=10), face = "bold",  size = 10),
    axis.ticks.x = element_line(),
    axis.ticks.length.x = unit(0.25,"cm"),
    text = element_text(family = "serif"),
    legend.title = element_blank(),
    legend.justification = "bottom",
                      legend.key.size = unit(0.5, "cm"),
                      legend.spacing.y = unit(0.05, 'cm'),
                      legend.text = element_text(face = "bold", size = 8),
                      # legend.box.margin=margin(0,0,0,30),
                        ggh4x.axis.ticks.length.minor = rel(0.5)
)
)

```

### Load template image file and convert to ggplot object

```{r template}
logo_file <- image_read("tsp_geosyntec_template.png")
image_gg <- ggdraw()+
  draw_image(logo_file, scale = 1)
logo_file
```

### Combine template, plot, and text annotations

```{r add plot layers and create final plot}
date_x_min = min(df_no_dupes$`Date Sampled`) #Min date for axis
date_x_max = max(df_no_dupes$`Date Sampled`) #Max date for axis

scaleFUN <- function(x) sprintf("%.1f", x)
# Annotating the Site, Figure number, name of analyte, and y-axis label from qrytable
plots_list <-   imap(.x=df_noDup_list, .f = ~(ggdraw()+
  draw_plot(image_gg) +
  annotate("text", x=.65, y=.205, label = unique(.$Site), size= 3, color ="black", hjust = 0) +
  annotate("text", x=.65, y=.225, label = paste("Time-Series Plot for ", unique(.$Plot)),  size= 3, color ="black", hjust = 0,
           fontface = "bold") +
  annotate("text", x=.89, y=.175, label = "Figure", size= 4, color ="black", hjust = 0,  vjust = 1)+
  annotate("text", x=.89, y=.13, label = stringr::str_wrap(unique(.$FigureNumber), 6), size= 4, color ="black", hjust = 0,  vjust = 1)+
  annotate("text", x=.765, y=.0855, label = figure_date, size= 3, color ="black", hjust = 0) +
  annotate("text", x=.62, y=.0855, label = figure_office, size= 3, color ="black", hjust = 0) +
  annotate("text", x=0.0475, y=0.085, label = figure_file_path, size= 1.5, color ="black",angle=90, hjust = 0) +
    draw_plot(ggplot(data=.x, aes(x=`Date Sampled`, y=SigFigResult, group=Loc)) +
                ylab(label = unique(.$Y_Label))+
                # scale_y_continuous( labels = scaleFUN)+
                # scale_y_log10(labels = fancyNumbers,
                #               breaks = prettyLogs)+
                scale_y_continuous(trans = 'log10', breaks = prettyLogs,labels = scaleFUN)+
                annotation_logticks(sides = "l", scaled = T, long=unit(5,"mm"))+
                scale_x_date(date_labels = "%b %Y",
                             limits = c(date_x_min,date_x_max),
                             date_minor_breaks = "1 year",
                             guide = "axis_minor") +
                geom_line(aes(color=Loc, linetype=Loc),
                          size=0.75)+
                geom_point(aes(color=Loc, shape= Detect),
                           size=3)+
                scale_shape_manual(values=c(1,16),drop = FALSE),
              x = 0.0725, y = 0.25, width = 0.88, height = 0.625)))

# Print one plot for us
plots_list$`Dissolved Oxygen`
plots_list$`1,2-Dichlorobenzene`

```

### Save plots in single pdf file

```{r ggsave}
# template_plots5 <- plots_list[1:5]

pdf("all_log.pdf",width = 11, 
       height = 8.5)
invisible(lapply(plots_list, print))
dev.off()
```